\documentclass[12pt]{article} 
\usepackage{graphicx}
\usepackage{color}
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}         %less than or approx. symbol
\textwidth=17cm \textheight=22.5cm   
\topmargin -1.5cm \oddsidemargin -0.3cm %\evensidemargin -0.8cm  
\begin{document}
We thank the referee for his careful reading of our paper and for his
last suggestions. We have corrected  all the  typos, and we have
addressed the four points that the referee raised, as we now explain.
\begin{enumerate}
\item{Of course, we meant exactly what the referee says, and we agree
  that the formulation was somewhat sloppy. We have now refromulated
  the sentence in order to make it more precise.
  }
\item{This was  a typo, 4FS showuld have been  matching conditions. We
  have now corrected the sentence .}
\item{This was indeed  a cut and paste error: the correct value of the
  massless limit of the 4FS is 138.8pb. Computing the difference as
  the referee says, we get that the  4F - 4F,0 term
  gives a $6-7\%$ increase of this contribution, which corrsponds to
  (less than) 1\% of the cross-section of Table~1.
The latter is of
  course the bottom fusion cross section as the referee says and we
  now state it explicitly.}
\item{We agree that this sentence was unnecessary and potentially
  confusing and we have just removed it as suggested by the referee.}
\end{enumerate}
We hope that we have addressed all the issues raised in a satisfactory
way and we believe that the paper has significantly improved as a
consequence of these changes.

\end{document}
